\documentclass[12pt]{article}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb,amsthm}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{geometry}

\setlength{\topmargin}{0pt}
\setlength{\headsep}{0pt}
\textheight = 600pt

\title{Probability Theory \\ Homework 1}
\author{Ben Kallus}
\date{Due Friday, September 4}

\begin{document}
\maketitle

\noindent {\bf Problem 1.}

    Let $E_n$ be the event that we roll an $n$.

    $\mathbb P(E_1) = \frac 2 5$.
    
    $\mathbb P(E_2) = \mathbb P(E_3) = \mathbb P(E_4) = \frac 1 5$.

\medskip
\noindent {\bf Problem 2.}

\noindent {\bf a.}

    $\mathbb P(A \cup B) = \mathbb P(A) + \mathbb P(B) + \mathbb P(A \cap B)$ because $\mathbb P(A \cap B)$ is contained within both $\mathbb P(A)$ and $\mathbb P(B)$, so we need to subtract off $\mathbb P(A \cap B)$ to prevent double counting.

\medskip
\noindent {\bf b.}

    Let $A$ be the event that the random student owns a parka.
    
    Let $B$ by the event that the random student owns boots.
    
    \begin{align*}
        \mathbb P(A \cup B) &= \mathbb P(A) + \mathbb P(B) - \mathbb P(A \cap B) \\
        .9 &= .6 + .8 - \mathbb P(A \cap B) \\
        .9 &= .6 + .8 - \mathbb P(A \cap B) \\
        -.5 &= - \mathbb P(A \cap B) \\
        \implies .5 &= \mathbb P(A \cap B)
    \end{align*}

\newpage
\noindent {\bf Problem 3.}

\noindent {\bf a.}

    The probability that we observe exactly 8 heads is $$\frac{{10 \choose 8}}{2^{10}}$$
    
\medskip
\noindent {\bf b.}

    There are $10 \choose 2$ ways to make exactly 2 wrong guesses, $10 \choose 1$ ways to make exactly 1 wrong guess, and $10 \choose 0$ ways to make no wrong guesses.
    
    Thus, there are ${10 \choose 2} + {10 \choose 1} + {10 \choose 0}$ total ways to make at least 8 correct guesses. Since there are $2^{10}$ ways to flip a coin ten times, the probability that you make at least 8 correct guesses is $\frac {{10 \choose 2} + {10 \choose 1} + {10 \choose 0}} {2^{10}}$.

\medskip
\noindent {\bf Problem 4.}

\noindent{\bf a.}

    The probability that the contestant picks $G$ on the very first guess is $\frac 1 3$. The probability that they pick $W$ on their first guess is $\frac 2 3$.
    
\medskip
\noindent{\bf b.}

    If their first guess was $G$, they win.
    
    If their first guess was $W$, they lose.
    
\medskip
\noindent{\bf c.}

    The probability of $G$ if the contestant keeps their original guess is $\frac 1 3$.
    
\medskip
\noindent{\bf d.}

    If their first guess was $G$, they lose. If their first guess was $W$, they win.
    
\medskip
\noindent{\bf e.}

    The probability of $G$ if the contestant switches doors is $\frac 2 3$.

\end{document}
