\documentclass[12pt]{article}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[margin=.75in]{geometry}
\usepackage{xcolor}
\usepackage{tikz}

\newtheorem{theorem}{Theorem}
\newtheorem{prop}{Proposition}
\newtheorem*{prop*}{Proposition}
\newtheorem{obs}{Observation}
\newtheorem*{obs*}{Observation}

\setlength{\topmargin}{0pt}
\setlength{\headsep}{0pt}
\textheight = 600pt

\title{Graph Theory \\ Homework 9}
\author{Ben Kallus and Nicholas Adair}
\date{Due Monday, Monday, March 15}

\begin{document}
\maketitle

\noindent{\bf 6.4}

{\bf (a)} $G = C_5$

{\bf (b)} $G = K_3$

{\bf (c)} $G = P_4$

{\bf (d)} $G = P_2$

{\bf (e)} $G:$
\begin{tikzpicture}
	\draw[fill=black] (0, 0) circle (3pt);
	\draw[fill=black] (1, 0) circle (3pt);
	\draw[fill=black] (2, 0) circle (3pt);
	\draw[fill=black] (1.5, 1) circle (3pt);

	\node at (.5, .25) {$e$};

	\draw[thick] (0,0) -- (1,0) -- (2,0) -- (1.5,1) -- (1,0);
\end{tikzpicture}

\newpage\noindent{\bf 6.6} Proposition: If $G$ be a connected regular graph that is not Eulerian, and $\overline{G}$ is connected, then $\overline{G}$ is Eulerian.
\begin{proof}
	Let $G$ be a connected $r$-regular graph of order $n$ that is not Eulerian such that $\overline G$ is connected.
	Since $G$ is not Eulerian, $r$ must be odd by Theorem 6.1.
	Then, by Corollary 2.3, $n$ is even.
	In any simple graph, a vertex's degree is at most $n - 1$.
	By the definition of $\overline G$, $\deg_G v + \deg_{\overline{G}} v = n - 1$.
	Thus, $$\deg_{\overline{G}} v = n - 1 - \deg_G v = n - 1 - r.$$
	Since $n$ is even and $r$ is odd, $n - 1 - r$ is even.
	Thus, every vertex of $\overline{G}$ has even degree.
	Therefore, by Theorem 6.1, $\overline{G}$ is Eulerian.
\end{proof}


\newpage\noindent{\bf 6.10} Proposition: If $G$ is a 6-regular graph of order 10, then for all $u,v \in V(G)$, $G$, $G - u$, and $G - u - v$ are all Hamiltonian.
\begin{proof}
	Let $G$ be a 6-regular graph of order 10.
	Then, $\delta(G) = 6 \geq \frac{10}2$.
	Thus, by Corollary 6.7, $G$ is Hamiltonian.

	Let $u \in V(G)$.
	Then, because $G$ is 6-regular, $G-u$ has 6 vertices of degree 5 and 3 vertices of degree 6.
	Thus, $\delta(G-u) = 5 \geq \frac{9}2$.
	Thus, by Corollary 6.7, $G-u$ is Hamiltonian.

	Let $v \in G-u$.
	Then, since $G-u$ consists only of degree 5 and 6 vertices, and contains only 3 degree-6 vertices, $v$ must be adjacent to a vertex of degree 5 in $G-u$.
	Thus, $\delta(G - u - v) = 4 \geq \frac{8}{2}$.
	Thus, by Corollary 6.7, $G-u-v$ is Hamiltonian.
\end{proof}

% You haven't yet shown that there are no cut-vertices. Just use the theorem about all paths between u and w and show that all non-adjacent vertices have a path through b and a path through c.
\newpage\noindent{\bf 6.14}

{\bf (a)}
\begin{proof} There exists a 2-connected Eulerian graph that is not Hamiltonian.
	Consider the following graph, $G$:
	\begin{center}
	\begin{tikzpicture}
		\draw[fill=black] (0,0) circle (3pt);
		\node at (0,.35) {$b$};
		\draw[fill=black] (1,1) circle (3pt);
		\node at (1,1.35) {$d$};
		\draw[fill=black] (2,0) circle (3pt);
		\node at (2,.35) {$c$};
		\draw[fill=black] (1,-1) circle (3pt);
		\node at (1,-.65) {$a$};
		\draw[fill=black] (1,-2) circle (3pt);
		\node at (1,-2.35) {$e$};
		\draw[thick] (0,0) -- (1,1) -- (2,0) -- (1,-1) -- (0,0) -- (1,-2) -- (2,0) -- (0,0);
	\end{tikzpicture}
	\end{center}

	$G$ is clearly connected.
	By Theorem 6.1, $G$ is Eulerian.
	Suppose that $G$ does have a cut-vertex $v$.
	Then, by Theorem 5.3, there exist distinct $u,w \in V(G) \setminus \{v\}$ such that every $u-w$ path in $G$ contains $v$.
	Thus, $u$ and $w$ are not adjacent.
	Therefore, $u$ is neither $b$ nor $c$, since $b$ and $c$ are adjacent to each other vertex in $G$.
	Similarly, $w$ is neither $b$ nor $c$.
	Thus, $u,w \in \{a,d,e\}$.
	Note that $(a,c,d)$ and $(a,b,d)$ are $a-d$ paths in $G$.
	Since the inner vertices of those paths are disjoint, it cannot be that $u = a$ and $w = d$.
	Since $a, d, e$ are in symmetric positions in $G$, a symmetric argument shows that $u$ and $w$ are not both in $\{a,d,e\}$.
	Thus, no $u,w$ satisfying the condition in Theorem 5.3 exists in $G$, so $G$ does not have a cut-vertex.
	Thus, $G$ is 2-connected.

	Suppose that $G$ were Hamiltonian.
	Then, $G$ contains a Hamiltonian cycle $C$ with first edge $ab$.\footnote{Since $b$ and $c$ are in symmetric positions, the same argument applies if the cycle starts with $ac$, instead.}
	Thus, since $a$ is incident to only two edges, $C$'s last edge must be $ca$.
	Note that $C$'s second edge must be one of $bd, be, bc$.
	Suppose that $C$'s second were $bc$.
	Then, since $C$'s last edge is $ca$, and $c$ cannot be repeated in $C$, it must be that $C = (a, b, c, a)$, which is not a Hamiltonian cycle.
	Thus, $C$'s second edge cannot be $bc$.
	Now, suppose that $C$'s second edge were $bd$.
	Then, $C$'s third edge must be $dc$.
	Then, by the same logic used previously, it must be that $C = (a, b, d, c, a)$, which is not a Hamiltonian cycle.
	Since $e$ and $d$ are in symmetric positions in $G$, the same argument shows that $C$'s second edge also cannot be $be$.
	Thus, no Hamiltonian cycle exists in $G$, so $G$ is not Hamiltonian.
\end{proof}

\newpage
{\bf (b)} There exists a Hamiltonian graph that is not Eulerian and has an Eulerian complement.
\begin{proof}
	Consider the following graph, $G:$
	\begin{center}
	\begin{tikzpicture}
		\draw[fill=black] (1.0, 0.0) circle (3pt);
		\node at (1.0, 0.35) {$a$};
		\draw[fill=black] (0.707, 0.707) circle (3pt);
		\node at (0.707, 1.057) {$b$};
		\draw[fill=black] (0.0, 1.0) circle (3pt);
		\node at (0.0, 1.35) {$c$};
		\draw[fill=black] (-0.707, 0.707) circle (3pt);
		\node at (-0.707, 1.057) {$d$};
		\draw[fill=black] (-1.0, 0.0) circle (3pt);
		\node at (-1.0, 0.35) {$e$};
		\draw[fill=black] (-0.707, -0.707) circle (3pt);
		\node at (-0.707, -1.10) {$f$};
		\draw[fill=black] (-0.0, -1.0) circle (3pt);
		\node at (0.0, -1.35) {$g$};
		\draw[fill=black] (0.707, -0.707) circle (3pt);
		\node at (0.707, -1) {$h$};
		
		\draw[thick] (1.0, 0.0) -- (-0.0, -1.0);
		\draw[thick] (1.0, 0.0) -- (0.707, 0.707);
		\draw[thick] (1.0, 0.0) -- (-1.0, 0.0);
		\draw[thick] (1.0, 0.0) -- (0.0, 1.0);
		\draw[thick] (1.0, 0.0) -- (0.707, -0.707);
		\draw[thick] (0.707, 0.707) -- (1.0, 0.0);
		\draw[thick] (0.707, 0.707) -- (-0.707, 0.707);
		\draw[thick] (0.707, 0.707) -- (0.0, 1.0);
		\draw[thick] (0.707, 0.707) -- (-0.707, -0.707);
		\draw[thick] (0.707, 0.707) -- (0.707, -0.707);
		\draw[thick] (0.0, 1.0) -- (-0.0, -1.0);
		\draw[thick] (0.0, 1.0) -- (1.0, 0.0);
		\draw[thick] (0.0, 1.0) -- (0.707, 0.707);
		\draw[thick] (0.0, 1.0) -- (-1.0, 0.0);
		\draw[thick] (0.0, 1.0) -- (-0.707, 0.707);
		\draw[thick] (-0.707, 0.707) -- (0.707, 0.707);
		\draw[thick] (-0.707, 0.707) -- (-1.0, 0.0);
		\draw[thick] (-0.707, 0.707) -- (0.0, 1.0);
		\draw[thick] (-0.707, 0.707) -- (-0.707, -0.707);
		\draw[thick] (-0.707, 0.707) -- (0.707, -0.707);
		\draw[thick] (-1.0, 0.0) -- (-0.0, -1.0);
		\draw[thick] (-1.0, 0.0) -- (1.0, 0.0);
		\draw[thick] (-1.0, 0.0) -- (-0.707, 0.707);
		\draw[thick] (-1.0, 0.0) -- (0.0, 1.0);
		\draw[thick] (-1.0, 0.0) -- (-0.707, -0.707);
		\draw[thick] (-0.707, -0.707) -- (-0.0, -1.0);
		\draw[thick] (-0.707, -0.707) -- (0.707, 0.707);
		\draw[thick] (-0.707, -0.707) -- (-1.0, 0.0);
		\draw[thick] (-0.707, -0.707) -- (-0.707, 0.707);
		\draw[thick] (-0.707, -0.707) -- (0.707, -0.707);
		\draw[thick] (-0.0, -1.0) -- (1.0, 0.0);
		\draw[thick] (-0.0, -1.0) -- (-1.0, 0.0);
		\draw[thick] (-0.0, -1.0) -- (0.0, 1.0);
		\draw[thick] (-0.0, -1.0) -- (-0.707, -0.707);
		\draw[thick] (-0.0, -1.0) -- (0.707, -0.707);
		\draw[thick] (0.707, -0.707) -- (-0.0, -1.0);
		\draw[thick] (0.707, -0.707) -- (1.0, 0.0);
		\draw[thick] (0.707, -0.707) -- (0.707, 0.707);
		\draw[thick] (0.707, -0.707) -- (-0.707, 0.707);
		\draw[thick] (0.707, -0.707) -- (-0.707, -0.707);
	\end{tikzpicture}
	\end{center}

	Observe that $(a,b,c,d,e,f,g,h,a)$ is a Hamiltonian path in $G$.
	Thus, $G$ is Hamiltonian.
	Since $G$ is 5-regular, $G$ is not Eulerian by Theorem 6.1.
	Note that $(a,d,g,b,e,h,c,f,a)$ is an Eulerian circuit in $\overline G$, so $\overline G$ is Eulerian.

\end{proof}

\newpage\noindent{\bf 6.16} Let $G$ be a connected $r$-regular graph of even order $n$ such that $\overline G$ is connected.

{\bf (a)} Proposition: Either $G$ or $\overline G$ is Eulerian.
\begin{proof}
	Suppose that neither $G$, nor $\overline G$ is Eulerian.
	Then, since $G$ is not Eulerian, by Theorem 6.1, $r$ is odd.
	Thus, $\overline G$ is $(n-1-r)$-regular.
	Since $n-1-r$ is even, $\overline G$ must be Eulerian, which contradicts our supposition.
	Thus, either $G$ or $\overline G$ is Eulerian.
\end{proof}

{\bf (b)} Proposition: Either $G$ or $\overline G$ is Hamiltonian.
\begin{proof}
	Suppose $r \geq \frac{n}{2}$.
	Then, $\deg_G v \geq \frac{n}{2}$ for all $v \in V(G)$.
	Thus, by Dirac's Theorem, $G$ is Hamiltonian.
	Now, suppose that $r < \frac{n}{2}$.
	Then, $\deg_G v < \frac{n}{2}$ for all $v \in V(G)$.
	Thus, since $\deg_G v$ is an integer, $\deg_G v \leq \frac n2 - 1$.
	By the definition of $\overline G$, $\deg_{\overline G}v = n - \deg_Gv-1$.
	Thus, $\deg_{\overline G}v \geq n - (\frac n2 - 1) - 1 = \frac n2$.
	Therefore, by Dirac's Theorem, $\overline{G}$ is Hamiltonian.
\end{proof}

\newpage\noindent{\bf 6.20} Proposition: If $G$ is a graph of order $n \geq 3$ with the property that for each $v \in V(G)$, there is a Hamiltonian path with initial vertex $v$, then $G$ is 2-connected and not necessarily Hamiltonian.
\begin{proof}
	Let $G$ be a graph of order $n \geq 3$ with the property that for each $v \in V(G)$, there is a Hamiltonian path with initial vertex $v$.
	Thus, since $G$ has a Hamiltonian path, it is connected.
	Let $x, y \in V(G)$.
	Then, there exists a Hamiltonian path $P = (x = p_0, \hdots, p_i = y, \hdots, p_n)$ starting at $x$.
	Thus, $P' = (x = p_0, \hdots, p_i = y)$ is an $x-y$ path in $G$, so $G$ is connected.
	Suppose that $G$ does have a cut-vertex $c$.
	Then, there exist $u,w \in V(G) \setminus \{v\}$ such that all $u-w$ walks contain $c$.
	Consider a Hamiltonian path $C$ with initial vertex $c$.
	Suppose, without loss of generality, that $u$ comes before $w$ in $C$.
	Consider $C'$, the subsequence of $C$ starting at $u$ and ending at $w$.
	Since $c$ is the initial vertex of $C$, it must not be present in $C'$.
	Thus, $C'$ is a $u-w$ walk that does not contain $c$, so not all $u-w$ walks contain $c$, which contradicts our supposition.
	Thus, $G$ must have no cut-vertices.
	Thus, $G$ is 2-connected.
\end{proof}
\begin{proof}
	Let $v$ be a vertex in the Petersen graph.
	Without loss of generality, suppose $v$ is in the ``outer shell" of the Petersen graph.\footnote{There is an isomorphism that maps the inner star of the Petersen graph to its outer shell, so this is safe to assume.}
	Then, a Hamiltonian path with inital vertex $v$ can be constructed by first following the edges along the outside of the Petersen graph, then following an edge to the inner star, and then following all edges in the inner star.
	Since all vertices in the Petersen graph are isomorphic, and it is clear that removing a single vertex from the graph does not disconnect it, the Petersen graph has no cut-vertices.
	Thus, since the Petersen graph is connected, it is 2-connected.
	However, by Theorem 6.5, the Petersen graph is not Hamiltonian.
	Thus, not all graphs with the property described above are Hamiltonian.
\end{proof}

\newpage\noindent{\bf 6.22}

	{\bf (a)} Yes.
	\begin{proof}
		$G = K_8 \cup N_2$ is an example of such a graph.
		$G$ has ${8 \choose 2} = 28$ edges.
		Since $G$ is disconnected, it must not be Hamiltonian.
	\end{proof}

	{\bf (b)} No.
	\begin{proof}
		By the Handshaking Lemma, the sum of the degrees of $H$ is $56$.
		Since $H$ has at least 5 vertices of degree 5, and at least 3 vertices of degree of 6, the last two vertices of $H$ must have a total degree of $$56 - 5 \cdot 5 - 3 \cdot 6 = 56 - 25 - 18 = 13.$$
    		Note that $\deg v \leq 9$ for any $v \in V(H)$, since $H$ is of order 10.
    		Thus, since $H$ is not Hamiltonian, Dirac's Theorem shows that one of the unknown vertices must be of degree at most $4$.
		Suppose that one of the unknown vertices has degree $d$ less than 4.
		Then, the other unknown vertex must have degree $13 - d > 9$, which is a contradiction.
		Thus, the degrees of the unknown vertices are $4$ and $9$.
		Thus, the degree sequence of $H$ is $(9, 6, 6, 6, 5, 5, 5, 5, 5, 4)$.
    
		Let $u$ be the degree-4 vertex in $H$.
		If $u$ were connected to a vertex of degree at less than, then $H$ would be Hamiltonian by Dirac's Theorem.
		Thus, we need only consider the case in which $u$'s neighbors are exactly those vertices of degree 6 or greater.
		Let $v$ be a vertex of degree 5 in $H$.
		Then, $v$ is not adjacent to $u$.
		Thus, there are 3 vertices in $H$ of degree at least 5 that are not adjacent to $v$.
		Then, by Theorem 6.8, $H$ is Hamiltonian if and only if $H+vw$ is Hamiltonian, for some $w \in V(G)$ of degree at least 5.
		By iteratively applying this process to each vertex of degree 5 in $H$, we find that $H$ is Hamiltonian if and only if a graph with one vertex of degree 4, and 9 vertices of degree greater than or equal to 6 is Hamiltonian.
		By Ore's Theorem, such a graph is Hamiltonian, so $H$ is Hamiltonian.
		Thus, no graph exists with the desired properties.
	\end{proof}
\newpage\noindent{\bf 6.24}
    {\bf (a)}
    \begin{proof}
	Let $G$ be a graph of order $2k+1$ with $k+1$ vertices of degree 2 and $k$ vertices of degree greater than 2, such that no two vertices of degree 2 are adjacent.
	Suppose that $G$ has a Hamiltonian cycle $C$.
	Consider the Hamiltonian path $P$ obtained by removing the final edge from $C$.
	In order for $P$ to contain all $k+1$ vertices of degree 2, it must have a single vertex of degree greater than 2 between each pair of vertices of degree 2.
	Since there are $k+1$ vertices of degree 2 and $k$ vertices of degree greater than 2, $P$ must begin and end with a vertex of degree 2.
	Thus, the final edge in $C$ runs between two vertices of degree 2, which contradicts the definition of $G$.
	Thus, $G$ is not Hamiltonian.
    \end{proof}

    {\bf (b)}
    \begin{proof}
	Let $H = K_2 + N_2$.
	Then, the vertices from $K_2$ have degree $3$ and the vertices from $N_2$ have degree $2$ in $H$.
	By Dirac's Theorem, $H$ is a Hamiltonian graph.
    \end{proof}


\newpage\noindent{\bf ALSO (1)} Proposition: If $r+s<t$, then $K_{r,s,t}$ is not Hamiltonian.
\begin{proof}
	Suppose $r + s < t$.
	Consider $S$, the subgraph of $K$ induced by its partite sets of order $r$ and $s$.
	Note that $|S| = r + s$.
	Define $T$ to be the subgraph of $K$ induced by the vertices of its partite set of order $t$.
	Then, $K_{r,s,t} - S = T$.
	Note that $k(T) = t$.
	Thus, by Theorem 6.5, $K_{r,s,t}$ is not Hamiltonian.
\end{proof}

\newpage\noindent{\bf ALSO (2)} Proposition: If $r+s \geq t$, then $K_{r,s,t}$ is Hamiltonian.
\begin{proof}
	Suppose that $r+s \geq t$.
	Define $R$, $S$, $T$ to be $K_{r,s,t}$'s partite sets of orders $r,s,t$ respectively.
	
	If $|T| = 1$, then $K_{r,s,t}$ contains all possible edges between vertices in $T$.
	Otherwise, let $t_1,t_2 \in T$.
	Then, $\deg(t_1) = \deg(t_2) = r + s$.
	Thus, $$\deg(t_1) + \deg(t_2) = r + s + r + s \geq r + s + t = n,$$ so $C(K_{r,s,t})$ contains the edge $t_1-t_2$.
	Thus, $C(K_{r,s,t})$ contains all possible edges between vertices in $T$.

	if $|S| = 1$, then $C(K_{r,s,t})$ contains all possible edges between vertices in $S$.
	Otherwise, let $s_1, s_2 \in S$. 
	Then, $\deg(s_1) = \deg(s_2) = r + t$.
	Thus, $$\deg(s_1) + \deg(s_2) = r + t + r + t \geq r + s + r + s \geq r + s + t = n,$$ so $C(K_{r,s,t})$ contains the edge $s_1-s_2$.
	Thus, $C(K_{r,s,t})$ contains all possible edges between vertices in $S$.

	If $|R| = 1$, then $C(K_{r,s,t})$ contains all possible edges between vertices in $R$.
	Otherwise, let $r_1, r_2 \in R$.
	Then, $\deg(r_1) = \deg(r_2) = s + t$.
	Thus, $$\deg(r_1) + \deg(r_2) = s + t + s + t \geq r + t + r + t \geq r + s + r + s \geq r + s + t = n,$$ so $C(K_{r,s,t})$ contains the edge $r_1-r_2$.
	Thus, $C(K_{r,s,t})$ contains all possible edges between vertices in $R$.

	Thus, $C(K_{r,s,t})$ is complete, so $K_{r,s,t}$ is Hamiltonian by Theorem 6.9.

\end{proof}
\end{document}
